Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-07-13 paper/paper.tex
updated references

\documentclass[a4,useAMS,usenatbib,usegraphicx]{mn2e} 
%=========================================================================
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{graphicx}
\usepackage{grffile}
\usepackage[dvips]{epsfig}
\usepackage{epsfig}  
\usepackage{color}
\usepackage{caption}
\usepackage[draft]{hyperref}
%Non reposionated tables

@@

% To highlight comments 
\definecolor{red}{rgb}{1,0.0,0.0}
\newcommand{\red}{\color{red}}
\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}
\newcommand{\before}[1]{\textcolor{red}{ #1}}
\newcommand{\after}[1]{\textcolor{darkgreen}{ #1}}
\newcommand{\hs}{{\hspace{1mm}}}  
\newcommand{\tol}{Tololo 1214-277}
\newcommand{\HI}{{\text{H\MakeUppercase{\romannumeral 1}}} }
\newcommand{\HII}{{\text{H\MakeUppercase{\romannumeral 2}}} }
\newcommand{\lya}{\ifmmode{{\rm Ly}\alpha}\else Ly$\alpha$\ \fi}
\newcommand{\cm}{\ifmmode{{\rm cm}}\else cm\fi}
\newcommand{\ccm}{\,\mathrm{cm}^{-3}}
\newcommand{\ergps}{\,{\rm erg}\,{\rm s}\ifmmode{}^{-1}\else ${}^{-1}$\fi}
\newcommand{\Mpch}{\,{\rm Mpc}\,\ifmmode h^{-1}\else $h^{-1}$\fi}
%\newcommand{\kms}{\,\mathrm{km}\,\mathrm{s}^{-1}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\vek}[1]{\bm{#1}}
%\newcommand{\lya}{Ly$\alpha$}
\newcommand{\hb}{H$\beta$}
\newcommand{\ha}{H$\alpha$}
\newcommand{\oiii}{[OIII]}
\newcommand{\oii}{[OII]}
\newcommand{\nii}{[NII]}
\newcommand{\esca}{erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$}
\newcommand{\esc}{erg cm$^{-2}$ s$^{-1}$}
\newcommand{\es}{erg s$^{-1}$}
\newcommand{\esa}{erg s$^{-1}$}
\newcommand{\kms}{\ifmmode\mathrm{km\ s}^{-1}\else km s$^{-1}$\fi}
\newcommand{\apj}{ApJ}  
\newcommand{\jcap}{JCAP}  
\newcommand{\apjs}{ApJS}  
\newcommand{\pasa}{PASA}  
\newcommand{\apjl}{ApJL}  
\newcommand{\aj}{AJ}  
\newcommand{\mnras}{MNRAS}  
\newcommand{\mnrassub}{MNRAS accepted}  
\newcommand{\aap}{A\&A}  
\newcommand{\aaps}{A\&AS}  
\newcommand{\araa}{ARA\&A}  
\newcommand{\nat}{Nature}  
\newcommand{\physrep}{PhR}
\newcommand{\pasp}{PASP}    
\newcommand{\pasj}{PASJ}    
\newcommand{\sigmaclump}{$54.3\pm 0.6$ km s$^{-1}$}
\newcommand{\inftyclump}{$54.3\pm 5.1$ km s$^{-1}$}
\newcommand{\probaclump}{$0.96\pm 0.01$}

@@

Star-forming Compact Dwarf Galaxies (CDGs) 
resemble the expected pristine conditions of the first galaxies in the
Universe and are the best systems to test models on primordial galaxy
formation and evolution. 
Here we report on one of such CDGs, \tol, which presents
a broad, single peaked, highly symmetric \lya emission line that had
evaded theoretical interpretation so far.  
In this paper we explain these features by two different physically
motivated kinematic models: 
an interstellar medium composed by outflowing clumps with 
random motions and an homogeneous gaseous sphere undergoing solid body
rotation.
It is the first time that an observed \lya spectrum can be explained
assuming either of these kinematic conditions.
The multiphase model requires a clump velocity dispersion of
at least \sigmaclump\ with outflows of \inftyclump\, while the
bulk rotation velocity is constrained to be $348^{+75}_{-48}$ \kms.
We argue that the multiphase model has more chances to be correct.
The clump velocity dispersion implies a dynamical mass of at least $2\times
10^{9}$ M$_{\odot}$, ten times its baryonic mass, which can be
explained if \tol\ is hosted by a dark matter halo of at least
$6\times 10^{11}$ M$_{\odot}$.
If future kinematic maps of \tol\ confirm the velocities suggested by the
multiphase model, it would provide additional support to expect this
condition to be present  in primordial \lya emitting galaxies.  
\end{abstract}

@@

However, the physical interpretation of \lya observations is
not straightforward \citep{LARS,2015ApJ...805...14R}. 
This is due to the resonant nature of the \lya line. 
A \lya photon follows a diffusion-like process before escaping
the galaxy or being absorbed by dust. 
The resulting line profile becomes sensitive to the dynamical, chemical
and thermal conditions in the interstellar medium. 
There are few analytical tools available to interpret the
emerging \lya line
\citep{Harrington73,1991ApJ...370L..85N,LoebRybicki,2006ApJ...645..792T}. 
They are applicable only in cases of highly symmetrical
conditions of the gaseous hydrogen distribution in the galaxy model,
which are hardly met in real astrophysical systems. 
For these reasons the interpretation of \lya observations
requires state-of-the-art Monte Carlo radiative transfer simulations.

@@

The main motivation for the outflowing multiphase model \citep[as presented
in][]{Gronke2016} is that some dwarf galaxies are expected to
present outflows.  
Observationally, outflows have been detected in few local dwarf galaxies
\citep{1998ApJ...506..222M,2005MNRAS.358.1453O}. 
Besides, clumpy multiphase outflows are capable to explain \lya features around
star-forming galaxies
\citep{2010ApJ...717..289S,2012MNRAS.424.1672D}.
In addition, due to the cooling properties of gas multiphase media are expected
in a range of astrophysical systems
\citep[][]{1977ApJ...218..148M,2016arXiv161001164M}.

The motivation for the rotation without outflows (as presented in
\cite{GaravitoCamargo2014}) is that dwarf galaxies show coherent
rotation features  \citep{2009A&A...493..871S} and it is expected that
some of them have high neutral gas contents with long quiescent phases
without high gas outflows triggered by supernova activity
\citep{2005A&A...433L...1B,2008ApJ...672..888T,2013MNRAS.434.2491G}.

@@

The idealized multiphase model consists of spherical, cold, dense
clumps of neutral hydrogen (and dust) embedded in a hot, ionized
medium \citep{Gronke2016}. 
The clumps also have a random and an outflowing velocity
component which totals the number of parameters describing the model
to be $14$.
We do not explore inflowing clumps given the slight line asymmetry
redwards to the line center (see the dots in Figure \ref{fig:results})
and thus set $v_{\infty,\,{\rm cl}}>0$.
The parameter description list is in Table \ref{tab:models}.

@@

We also a Kolmogorov-Smirnov (K-S) test to compare each parameter
distribution in the best $25$ models against the parent distribution
of $2500$ models. 
From a p-value $<0.05$ for a given model parameter, we conclude that
this parameter can be constrained from the observations, as the distribution for
the best $\chi^2$ models is statistically different to the
distribution from the global sample of $2500$ models.

We finally compute the best values for the constrained parameters as
the values that produce the minimum $\chi^2$.  
We estimate the 1-$\sigma$ uncertainty from a parabolic fit to the
$\chi^2$ as a function of the constrained parameters around its
corresponding minimum.

@@

The rotation model corresponds to the work presented in
\citep{GaravitoCamargo2014} based on the Monte Carlo code
\texttt{CLARA} \citep{CLARA}. 
In that model the \lya photons are propagated 
within a spherical and homogeneous cloud of HI gas undergoing solid
body rotation.
The sphere is fully characterized by three parameters: the HI line's
center optical  depth $\tau$ measured from the center to its surface, the HI
temperature $T$, and the linear surface velocity $V_{\rm max}$.  
The observed line profile also depends on $\theta$,  the angle between the plane
perpendicular to the rotation axis and the observational
line-of-sight.  
In this model, dust only changes the overall line
normalization and only weakly its shape, i.e. 
dust cannot change the line symmetry or induce a change in the number
of line peaks, moreover it does not change the line width by more than
$1\%$ ($5$ \kms\ in the case of \tol), an effect too small to be
observed at the resolution at which we have \tol's line profile and
also negligible compared to the influence of the other free parameters in the model.
For these reasons we do not include any dust model.

@@

With $14$ free parameters our first concern is discovering which 
parameters matter the most.
From the K-S tests we find that only 3 parameters 
are confidently constrained by \tol's line shape;
$v_{\infty,\rm{cl}}$ (p-value  $10^{-18}$), $\sigma_{\rm cl}$ (p-value
$10^{-4}$) $P_{\rm cl}$ (p-value $10^{-4}$).

This illustrated by the results shown in Figure \ref{multiphaseresults}.
Left column shows the difference between the integrated distributions
of the full sample (2500 input models) and the $1\%$ models with the lowest
$\chi^2/d.o.f.$.  
The right column shows the actual $\chi^2/d.o.f.$ 
and its corresponding parameter value. 
Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.
\mg{These errors seem still pretty small to me. You obtained these via a Fisher matrix of a parabolic fit, right? How good was the fit? Are the off-diagonal elements included?}
\jefr{The small uncertainty only says that the increase in
  $\chi^2/dof$ is very steep as you vary a parameter. I don't think you can get larger errors
  with the available data. Simple inspection of Figure 2 shows
  that the errors will be small with the data we have. The
  paremeter uncertainty roughly corresponds to the width of the parabola
  when there is a difference of $\chi^2/dof\sim 1$ from the minimum. In the data we
  have a huge jump of $\chi^2/dof$ of $\sim 5$ between the minimum
  and the nearest data point. }

Qualitatively this result can be understood as follows.
Due to the large fraction of \lya photons being emitted within the
moving clumps ($P_{\rm cl}\sim 1$) the `intrinsic' profile follows 
the clump kinematics. In other words, the width of the intrinsic line
is set by $\sigma_{\mathrm{cl}}$ and its median offset mainly by
$v_{\infty,{\rm cl}}$ and $\beta_{\rm cl}$.. 
Furthermore, the relatively low mean number of clumps per line of
sight, $f_{\mathrm{cl}}$, combined with the high velocity dispersion
of the clumps implies existence of low-density inter-clump 
regions where \lya photons can freely propagate.
This gives result to an emergent spectrum close to the intrinsic one, explaining the high
flux at line center as observed.

Because the width of the observable spectrum is hence set primarily by
$\sigma_{\rm cl}$, a lower velocity dispersion would produce a
narrower line and thus a worse fit. 
From the lower right panel in Figure \ref{multiphaseresults} we find that it
is unlikely that the clump velocity dispersion is lower than
$50$ \kms.

@@

\jefr{I find this paragraph confusing. Discussing an hypotetical case where
all parameters matter undermines the explanation of our concrete case
where only some parameters matter more. Probably we can remove it}.
{\bf However, larger values of $f_{\rm cl}$ -- outside the here considered parameter range -- would re-introduce
additional radiative transfer effects and thus increase the number of
relevant parameters \citep[see ][for details]{2017arXiv170406278G}.   
This means that even  
if for clumply models the line profile is most sensitive to only
a few parameters \citep{Gronke2016}, the rest of parameters
affect the line profile at a level that cannot be neglected.}

As a test we run a small set of $100$ additional radiative
transfer simulations with random values for all parameters, except for
$\sigma_{\rm cl}$, $P_{\rm cl}$ which are kept within the derived $3\sigma$
constraints. We find that $30$ models show $\chi^2/d.o.f.<35$.
That is, we have a $30\%$ chance to find good models, which is
significanty higher than the lower $1\%$ success rate if the
parameters were unconstrained.  
\mg{Is $1\sigma$ correct?}\jefr{I checked and only $\sigma_{cl}$ and
  $P_{cl}$ were run within $3\sigma$. All the other parameters,
  including $v_{\infty}$, were
  unconstrained.}

However, we cannot discard that another region of parameter space
could also yield a good fit to the observed line-profile.
This might be interesting to explore in the
future with, e.g., a higher sampling of the parameter space once new 
observations  clarify the kinematic nature of \tol.In
  Section \S \ref{sec:conclusions} we describe  in more detail what
  kind of observations could be performed in the near future to
  improve our understanding of \tol's kinematics.

@@

Which model has more
chances to be correct?  
We discard the rotation model by considering that the prefered rotational
velocity of $V_{m}\sim350$ \kms is of the same order as the largest rotational velocity of giant
disc galaxies that have two orders of magnitude more baryonic mass
than \tol\ \citep{2015MNRAS.448.1767C}. 
\mg{I am confused -- are much lower rotational
  velocities not exclude by the priors used?}\jefr{Yes, they are
  discarded, but here we are talking about the most likely value of
  350 km/s.}

Furthermore, \tol's structural properties seem to be similar to known dwarf
elliptical galaxies. 
The sample of 7 dwarf ellipticals (dE) observed by
\cite{2003AJ....126.1794G} show similar properties as \tol. 
For instance, the dE galaxies IC 3344 and IC 794 have similar absolute $M_V$
magnitudes (-17.10 and -17.19) and sizes (0.90 kpc and 0.82 kpc) as
\tol. 
These dE galaxies have velocity dispersions of $31.1$ \kms and
$44.6$ \kms, respectively,  and their rotational velocities are lower
than $1$ \kms.  
This leads us to prefer the multiphase model as it provides 
a broad consistency with kinematic properties of dE galaxies.

@@

Assuming that the \lya emission is entirely powered by star formation 
we use the 3D half-light radius $r_s=2.25$ kpc as the typical size
for the HI region, in the multiphase model the clump velocity dispersion
$\sigma_{\rm{cl}}=$\sigmaclump thus corresponds to a dynamical mass of
$M_{\rm dyn}=2.31\pm0.04 \times 10^{9}$ $M_{\odot}$, which is ten
times the estimated baryonic mass in \tol.
Considering that the results for $\sigma_{\rm{cl}}$ are most probably
a lower bound, the results for the dynamical mass should also be
considered as a lower bound.

Figure \ref{fig:mass} illustrates  how such dynamical
mass can be explained if \tol\ is hosted by a dark matter halo of at
least $6\times 10^{11}$ M$_{\odot}$ in virial mass. 
This estimate is based on computing the integrated mass profile of a
spherical dark matter halo with a Navarro-Frenk-White profile with its
concentration following the median mass-concentration
relationship found in the Bolshoi simulation
\citep{2012MNRAS.423.3018P,2016ApJ...832..169P}.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.46\textwidth]{enclosed_mass.pdf}
\caption{Enclosed mass in a spherical system as a function of radius.
  Lines correspond to the expectation for dark matter halos with
  different viral masses as shown in the legend, the arrow corresponds
  to the dynamical mass lower bounds for \tol.  
  The dynamical mass estimates for \tol\ are consistent with the
  galaxy being hosted by a dark matter halo of at least
  $6\times10^{11}$ M$_{\odot}$ in mass.
    \label{fig:mass}} 
\end{center}
\end{figure}

@@

\section*{Acknowledgments}
We thank the referee for detailed comments and suggestions that
improved this paper. 
We thank J. M. Mas-Hesse for providing us with \tol's observational
\lya data \citep{mashesse03} in electronic format. This data was
used to prepare Figure 1.
J. E. F-R. acknowledges the support of J. L. Guerra in the last
writing stages of this paper.

\bibliographystyle{mn2e}
%\bibliography{references}

@@

As a complement to the K-S tests on the multiphase data 
we apply a random forest classification algorithm to find the
more relevant parameters in the model to produce a low $\chi^2$
result.

%Using the total number of degrees of freedom, $d.o.f.=104$ 
We divide
the results in two classes: low $\chi^2/d.o.f.<35$ and high
$\chi^2/d.o.f.>35$. \mg{Why was $35$ chosen as a boundary?}\jefr{We
  chose $35$ to match the cut that we used to make the  integrated
  probability distributions. However the nuber itself is
  arbitrary to have the $1\%$ of the initial number of models. 
Ideally we should only chose models with $\chi^/dof$
  higher by $2$ than the lowest $\chi^2/dof$, but we don't have any
  models in that range.}
The algorithm uses $500$ trees for the classification and a
maximum of $3$ depth levels. 
To check for stability we repeat the computation $10$ times by
randomly subsampling the input data to use $80\%$ of the data as
the training set.

@@

Furthermore, considering the sparse sampling of parameter space and the results
from the random forest classifier, it is safer to consider that
the best values for $\sigma_{\rm cl}$, $v_{\infty {\rm cl}}$, $P_{\rm
  cl}$ are actually lower/upper/lower bounds, respectively.
\mg{This is interesting. Why do you think that? Could we use that to
  increase the quoted errors? I am worried that the referee will
  complain about the small errors.} \jefr{The referee didn't complain
  about the small errors.}

>>>>

\documentclass[a4paper,fleqn,usenatbib]{mnras}
%=========================================================================
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{graphicx}
\usepackage{grffile}
\usepackage[dvips]{epsfig}
\usepackage{epsfig}  
\usepackage{color}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{bm}
%Non reposionated tables

@@

% To highlight comments 
\definecolor{red}{rgb}{1,0.0,0.0}
\newcommand{\red}{\color{red}}
\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}
\newcommand{\before}[1]{\textcolor{red}{ #1}}
\newcommand{\after}[1]{\textcolor{darkgreen}{ #1}}
\newcommand{\hs}{{\hspace{1mm}}}  
\newcommand{\tol}{Tololo 1214-277}
\newcommand{\HI}{{\text{H\MakeUppercase{\romannumeral 1}}} }
\newcommand{\HII}{{\text{H\MakeUppercase{\romannumeral 2}}} }
\newcommand{\lya}{\ifmmode{{\rm Ly}\alpha}\else Ly$\alpha$\ \fi}
\newcommand{\cm}{\ifmmode{{\rm cm}}\else cm\fi}
\newcommand{\ccm}{\,\mathrm{cm}^{-3}}
\newcommand{\ergps}{\,{\rm erg}\,{\rm s}\ifmmode{}^{-1}\else ${}^{-1}$\fi}
\newcommand{\Mpch}{\,{\rm Mpc}\,\ifmmode h^{-1}\else $h^{-1}$\fi}
%\newcommand{\kms}{\,\mathrm{km}\,\mathrm{s}^{-1}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\vek}[1]{\bm{#1}}
%\newcommand{\lya}{Ly$\alpha$}
\newcommand{\hb}{H$\beta$}
\newcommand{\ha}{H$\alpha$}
\newcommand{\oiii}{[OIII]}
\newcommand{\oii}{[OII]}
\newcommand{\nii}{[NII]}
\newcommand{\esca}{erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$}
\newcommand{\esc}{erg cm$^{-2}$ s$^{-1}$}
\newcommand{\es}{erg s$^{-1}$}
\newcommand{\esa}{erg s$^{-1}$}
\newcommand{\kms}{\ifmmode\mathrm{km\ s}^{-1}\else km s$^{-1}$\fi}
\newcommand{\sigmaclump}{$54.3\pm 0.6$ km s$^{-1}$}
\newcommand{\inftyclump}{$54.3\pm 5.1$ km s$^{-1}$}
\newcommand{\probaclump}{$0.96\pm 0.01$}

@@

Star-forming Compact Dwarf Galaxies (CDGs) 
resemble the expected pristine conditions of the first galaxies in the
Universe and are the best systems to test models on primordial galaxy
formation and evolution. 
Here we report on one of such CDGs, \tol, which presents
a broad, single peaked, highly symmetric \lya emission line that had
evaded theoretical interpretation so far.  
In this paper we explain these features by two different physically
motivated kinematic models: 
an interstellar medium composed by outflowing clumps with 
random motions and an homogeneous gaseous sphere undergoing solid body
rotation.
It is the first time that an observed \lya spectrum can be explained
assuming either of these kinematic conditions.
The multiphase model requires a clump velocity dispersion of
\sigmaclump\ with outflows of \inftyclump\, while the
bulk rotation velocity is constrained to be $348^{+75}_{-48}$ \kms.
We argue that the multiphase model has more chances to be correct.
The clump velocity dispersion implies a dynamical mass of $2\times
10^{9}$ M$_{\odot}$, ten times its baryonic mass, which can be
explained if \tol\ is hosted by a dark matter halo $6\times 10^{11}$
M$_{\odot}$. If future kinematic maps of \tol\ confirm the velocities
suggested by the multiphase model, it would provide additional support
to expect this condition to be present  in primordial \lya emitting
galaxies.   
\end{abstract}

@@

However, the physical interpretation of \lya observations is
not straightforward \citep{LARS,2015ApJ...805...14R}. 
This is due to the resonant nature of the \lya line. 
A \lya photon follows a diffusion-like process before escaping
the galaxy or being absorbed by dust. 
The resulting line profile becomes sensitive to the dynamical, chemical
and thermal conditions in the interstellar medium. 
There are few analytical tools available to interpret the
emerging \lya line
\citep{Harrington73,1991ApJ...370L..85N,LoebRybicki,2006ApJ...645..792T}. 
They are applicable only in highly idealized conditions that
are hardly met in real astrophysical systems. 
For these reasons the interpretation of \lya observations
requires state-of-the-art Monte Carlo radiative transfer simulations.

@@

The main motivation for the outflowing multiphase model \citep[as presented
in][]{Gronke2016} is that some dwarf galaxies are expected to
present outflows.  
Observationally, outflows have been detected in few local dwarf galaxies
\citep{1998ApJ...506..222M,2005MNRAS.358.1453O}. 
Besides, clumpy multiphase outflows are capable to explain \lya features around
star-forming galaxies
\citep{2010ApJ...717..289S,2012MNRAS.424.1672D}.
In addition, due to the cooling properties of gas, multiphase media are expected
in a range of astrophysical systems
\citep[][]{1977ApJ...218..148M,2016arXiv161001164M}.

The motivation for the rotation without outflows as presented in
\citep[as presented in]{GaravitoCamargo2014} is that dwarf galaxies show coherent
rotation features  \citep{2009A&A...493..871S} and it is expected that
some of them have high neutral gas contents with long quiescent phases
without high gas outflows triggered by supernova activity
\citep{2005A&A...433L...1B,2008ApJ...672..888T,2013MNRAS.434.2491G}.

@@

The idealized multiphase model consists of spherical, cold, dense
clumps of neutral hydrogen and dust embedded in a hot, ionized
medium \citep{Gronke2016}. 
The clumps also have a random and an outflowing velocity
component which totals the number of parameters describing the model
to be $14$.
We do not explore inflowing clumps given the slight line asymmetry
redwards to the line center (see the dots in Figure \ref{fig:results})
and thus set $v_{\infty,\,{\rm cl}}>0$.
The parameter description list is in Table \ref{tab:models}.

@@

We run a Kolmogorov-Smirnov (K-S) test to compare each parameter
distribution in the best $25$ models against the parent distribution
of $2500$ models. 
If we obtain a p-value $<0.05$ we conclude that
this parameter can be constrained from the observations, as the distribution for
the best $\chi^2$ models is statistically different to the
distribution from the global sample of $2500$ models.  
In the Appendix \ref{appendix} we complement this analysis using a
random forest classifier to find the most important parameters in
selecting a low $\chi^2$ model.

We finally compute the best values for the constrained parameters as
the values that produce the minimum $\chi^2$.  
We estimate the 1-$\sigma$ uncertainty from a parabolic fit to the
$\chi^2$ as a function of the best constrained parameters around its
corresponding minimum.

@@

The rotation model corresponds to the work presented by
\cite{GaravitoCamargo2014} based on the Monte Carlo code
\texttt{CLARA} \citep{CLARA}. 
In that model the \lya photons are propagated 
within a spherical and homogeneous cloud of HI gas undergoing solid
body rotation.
The sphere is fully characterized by three parameters: the HI line's
center optical  depth $\tau$ measured from the center to its surface, the HI
temperature $T$, and the linear surface velocity $V_{\rm max}$.  
The observed line profile also depends on $\theta$,  the angle between the plane
perpendicular to the rotation axis and the observational
line-of-sight.  
In this model, dust only changes the overall line
normalization and only weakly its shape, i.e. 
dust cannot change the line symmetry or induce a change in the number
of line peaks, moreover it does not change the line width by more than
$1\%$ ($5$ \kms\ in the case of \tol), an effect too small to be
observed at the resolution at which we have \tol's line profile and
also negligible compared to the influence of the other free parameters in the model.
For these reasons we do not include any dust model.

@@

With $14$ free parameters our first concern is discovering which 
parameters matter the most.
From the K-S tests we find that only 3 parameters 
are confidently constrained by \tol's line shape;
$v_{\infty,\rm{cl}}$ (p-value  $10^{-18}$), $\sigma_{\rm cl}$ (p-value
$10^{-4}$) and $P_{\rm cl}$ (p-value $10^{-4}$).

The low p-values are illustrated by the results shown in Figure \ref{multiphaseresults}.
Left column shows the difference between the integrated distributions
of the full sample (2500 input models) and the $1\%$ models with the lowest
$\chi^2/d.o.f.$, where we use the total number of degrees of freedom,
$d.o.f.=104$. 
The right column shows the actual $\chi^2/d.o.f.$ 
and its corresponding parameter value. 
Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.
\mg{These errors seem still pretty small to me. You obtained these via a Fisher matrix of a parabolic fit, right? How good was the fit? Are the off-diagonal elements included?}
\jefr{The small uncertainty only says that the increase in
  $\chi^2/dof$ is very steep as you vary a parameter. I don't think you can get larger errors
  with the available data. Simple inspection of Figure 2 shows
  that the errors will be small with the data we have. The
  paremeter uncertainty roughly corresponds to the width of the parabola
  when there is a difference of $\chi^2/dof\sim 1$ from the minimum. In the data we
  have a huge jump of $\chi^2/dof$ of $\sim 5$ between the minimum
  and the nearest data point. }

Qualitatively this result can be understood as follows.
Due to the large fraction of \lya photons being emitted within the
moving clumps ($P_{\rm cl}\sim 1$) the `intrinsic' profile follows 
the clump kinematics. In other words, the width of the intrinsic line
is set by $\sigma_{\mathrm{cl}}$ and its median offset mainly by
$v_{\infty,{\rm cl}}$ and $\beta_{\rm cl}$.
Furthermore, the relatively low mean number of clumps per line of
sight, $f_{\mathrm{cl}}$, combined with the high velocity dispersion
of the clumps implies existence of low-density inter-clump 
regions where \lya photons can freely propagate.
This gives result to an emergent spectrum close to the intrinsic one, explaining the high
flux at the line's center.

Because the width of the observable spectrum is hence set primarily by
$\sigma_{\rm cl}$, a lower velocity dispersion would produce a
narrower line and thus a worse fit. 
From the lower right panel in Figure \ref{multiphaseresults} we find
that in fact it is unlikely that the clump velocity dispersion is
lower than $50$ \kms.

@@

\jefr{I find this paragraph confusing. Discussing an hypotetical case where
all parameters are important undermines the explanation of our concrete case
where only some parameters matter more. Probably we can remove it}.
{\bf However, larger values of $f_{\rm cl}$ -- outside the here considered parameter range -- would re-introduce
additional radiative transfer effects and thus increase the number of
relevant parameters \citep[see ][for details]{2017arXiv170406278G}.   
This means that even  
if for clumply models the line profile is most sensitive to only
a few parameters \citep{Gronke2016}, the rest of parameters
affect the line profile at a level that cannot be neglected.}

{\bf As a test we run a small set of $100$ additional radiative
transfer simulations with random values for all parameters, except for
$\sigma_{\rm cl}$, $P_{\rm cl}$ which are kept within the derived $3\sigma$
constraints. We find that $30$ models show $\chi^2/d.o.f.<35$.
That is, we have a $30\%$ chance to find good models, which is
significanty higher than the lower $1\%$ success rate if the
parameters were unconstrained.  }
\mg{Is $1\sigma$ correct?}\jefr{I checked and only $\sigma_{cl}$ and
  $P_{cl}$ were run within $3\sigma$. All the other parameters,
  including $v_{\infty}$, were
  unconstrained. Should we mention this test given that we didn't run
  with a constrain on $v_{\infty}$?}

However, we cannot discard that another region of parameter space
could also yield a good fit to the observed line-profile.
This might be interesting to explore in the
future with, e.g., a higher sampling of the parameter space once new 
observations  clarify the kinematic nature of \tol. 
In Section \S \ref{sec:conclusions} we describe  in more detail what
kind of observations could be performed in the near future to improve
our understanding of \tol's kinematics.

@@

Which model has more
chances to be correct?  
We argue that that the rotation model should be discarded by
considering that the prefered rotational velocity of $V_{m}\sim350$
\kms\ is of the same order as the largest rotational velocity of giant
disc galaxies that have two orders of magnitude more baryonic mass
than \tol\ \citep{2015MNRAS.448.1767C}.  
\mg{I am confused -- are much lower rotational
  velocities not exclude by the priors used?}\jefr{Yes, they are
  discarded, but here we are talking about the most likely value of
  350 km/s.}

Furthermore, \tol's structural properties seem to be similar to known dwarf
elliptical (dE) galaxies. 
The sample of 7 dE galaxies observed by
\cite{2003AJ....126.1794G} shows similar properties as \tol. 
For instance, the dE galaxies IC 3344 and IC 794 have similar absolute $M_V$
magnitudes (-17.10 and -17.19) and sizes (0.90 kpc and 0.82 kpc) as
\tol. 
These dE galaxies have velocity dispersions of $31.1$ \kms and
$44.6$ \kms, respectively,  and their rotational velocities are lower
than $1$ \kms.  
This leads us to prefer the multiphase model as it provides 
a broad consistency with kinematic properties of dE galaxies.

@@

Assuming that the \lya emission is entirely powered by star formation 
we use the 3D half-light radius $r_s=2.25$ kpc as the typical size
for the HI region, in the multiphase model the clump velocity dispersion
$\sigma_{\rm{cl}}=$\sigmaclump thus corresponds to a dynamical mass of
$M_{\rm dyn}=2.31\pm0.04 \times 10^{9}$ $M_{\odot}$, which is ten
times the estimated baryonic mass in \tol.

Figure \ref{fig:mass} illustrates  how such dynamical
mass can be explained if \tol\ is hosted by a dark matter halo of at
$\sim 6\times 10^{11}$ M$_{\odot}$ in virial mass. 
This estimate is based on computing the integrated mass profile of a
spherical dark matter halo with a Navarro-Frenk-White profile with its
concentration following the median mass-concentration
relationship found in the Bolshoi simulation
\citep{2012MNRAS.423.3018P,2016ApJ...832..169P}.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.46\textwidth]{enclosed_mass.pdf}
\caption{Enclosed mass in a spherical system as a function of radius.
  Lines correspond to the expectation for dark matter halos with
  different viral masses as shown in the legend, the arrow corresponds
  to the dynamical mass lower bounds for \tol.  
  The dynamical mass estimates for \tol\ are consistent with the
  galaxy being hosted by a dark matter halo of
  $\sim 6\times10^{11}$ M$_{\odot}$ in mass.
    \label{fig:mass}} 
\end{center}
\end{figure}

@@

\section*{Acknowledgments}
We thank the referee for detailed comments and suggestions that
improved this paper. 
We thank J. M. Mas-Hesse for providing us with \tol's observational
\lya data \citep{mashesse03} in electronic format. This data was
used to prepare Figure 1.
J. E. F-R. acknowledges the support of J. L. Guerra in the last
writing stages of this paper.
We are thankful to the community developing and maintining open source
packages fundamental to our work: Jupyter notebook \citep{IPython,jupyter},
matplotlib \citep{matplotlib}, astropy \citep{astropy} and
scikit-learn \citep{scikit-learn}.

\bibliographystyle{mnras}
\bibliography{references}

@@

As a complement to the K-S tests on the multiphase data 
we apply a random forest classification algorithm
\citep{james2014introduction} to find the
more relevant parameters in the model to produce a low $\chi^2$
result.

We divide
the results in two classes: low $\chi^2/d.o.f.<35$ and high
$\chi^2/d.o.f.>35$, that is the limit that divides the best $1\%$ of
the models from the rest. \mg{Why was $35$ chosen as a boundary?}\jefr{We
  chose $35$ to match the cut that we used to make the  integrated
  probability distributions. However the nuber itself is
  arbitrary to have the $1\%$ of the initial number of models. 
Ideally we should only chose models with $\chi^/dof$
  higher by $2$ than the lowest $\chi^2/dof$, but we don't have any
  models in that range.}
The algorithm uses $500$ trees for the classification and a
maximum of $3$ depth levels. 
To check for stability we repeat the computation $10$ times by
randomly subsampling the input data to use $80\%$ of the data as
the training set.

@@

{\bf Furthermore, considering the sparse sampling of parameter space and the results
from the random forest classifier, it is safer to consider that
the best values for $\sigma_{\rm cl}$, $v_{\infty {\rm cl}}$, $P_{\rm
  cl}$ are actually lower/upper/lower bounds, respectively.}
\mg{This is interesting. Why do you think that? Could we use that to
  increase the quoted errors? I am worried that the referee will
  complain about the small errors.} \jefr{The referee didn't complain
  about the small errors. And now that I see this with a bit more of
  perspective, the tree classification always work with 'larger
  than/less than' dualities. It would be unfair/unjustified to use that to justify
our results as a lower bound. I suggest we remove this paragraph.}
